An early warning system for monitoring stress in the financial system

### 2016-10-09 srisk9.tex
Lots and lots of changes
Latest

\begin{abstract}
SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework and exploiting time series methods.  Baseline risk and the stress risk  are in terms of time series based ordinary and stressed expectation.  Stressed expectation is expectation computed  under a hypothetical  stress, modelled with a stress function and scenarios.  Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.  Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.    Properties and characterisations of stress and stress related quantities are displayed and explored.     Application is made to the study of the stability of Australian banks using daily time series data.
\end{abstract}

>>>>

\begin{abstract}
SRISK methodology recently proposed in the literature is refined and extended using a formalised stress testing framework.  The framework defines two types of risk:  baseline risk and the stress risk, corresponding to ordinary and ``stressed" expectation, respectively, given a time series model and past observations.   Stressed expectation is expectation computed  under a hypothetical  stress, modelled with a stress function and scenarios.   Stress functions are chosen by the practitioner and  exaggerate the probability undesirable  outcomes.    Properties and characterisations of stress and stress related quantities are displayed and explored.  Systemic stress is defined in terms of stresses   impacting groups of firms or financial entities.    Application is made to the study of the stability of Australian banks using daily time series data.
\end{abstract}
